Edge sign prediction in general graphs and Correlation Clustering

### 2017-09-05 troll/generative.tex
add one picture for generative model

We now define the stochastic generative model for edge labels we use in the batch learning setting.
Given the graph $G = (V,E)$, let the label $\yuv \in \spin$ of directed edge $(u,v) \in E$ be
generated as follows. Each node $u \in V$ is endowed with two latent parameters $p_u, q_u \in
[0,1]$, which we assume to be generated, for each node $u$, by an independent draw from a fixed but
unknown joint prior distribution $\mu(p,q)$ over $[0,1]^2$. Each label $\yuv \in \spin$ is then
generated by an independent draw from the mixture of $p_u$ and $q_v$
$$\Pr\big( \yuv = 1 \big) = \tfrac{p_u + q_v}{2}$$

>>>>

We now define the stochastic generative model for edge labels we use in the batch learning setting.
Given the graph $G = (V,E)$, let the label $\yuv \in \spin$ of directed edge $(u,v) \in E$ be
generated as follows. Each node $u \in V$ is endowed with two latent parameters $p_u, q_u \in
[0,1]$, which we assume to be generated, for each node $u$, by an independent draw from a fixed but
unknown joint prior distribution $\mu(p,q)$ over $[0,1]^2$. Each label $\yuv \in \spin$ is then
generated by an independent draw from the mixture of $p_u$ and $q_v$
$$\Pr\big( \yuv = 1 \big) = \tfrac{p_u + q_v}{2}$$
This can be seen pictorially in \autoref{fig:troll_genmodel}.
\begin{marginfigure}
	\centering
	\includegraphics[width=0.98\linewidth]{tikz/troll_genmodel_tikz}
	\caption{The sign \yuv{} of the edge \euv{} is positive with probability $\frac{1}{2}(p_u+q_v)$.
	\label{fig:troll_genmodel}}
\end{marginfigure}
